%-------------------------
% Resume in Latex
% Original Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Swastik Baranwal} \\ \vspace{1pt}
    \small ~ \href{https://swastik.is-a.dev}{\raisebox{-0.2\height}\faLink\  \underline{swastik.is-a.dev}} ~
    \small ~ \href{mailto:swstkbaranwal@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{swstkbaranwal@gmail.com}} ~ 
    \href{https://linkedin.com/in/swastik-baranwal/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/swastik-baranwal}}  ~
    \href{https://github.com/Delta456}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/Delta456}}
    \vspace{-8pt}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
          {\href{https://vlang.io/}{The V Programming Language Organization}}{August 2022 -- Present}
      {Core Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Working as a paid \textbf{part-time} open source developer for \textbf{The V Programming Language}.}
        \resumeItem{Fixed \textit{several} checker, parser, scanner, and code generation-related issues.}
        \resumeItem{Implemented features like \textbf{operator overloading}, \textbf{syntax highlighting for v doc}, \textbf{match branch range expressions with constants}, \textbf{non-string map keys}, etc.}
        \resumeItem{Documented and developed \textit{several} internal libraries.}
      \resumeItemListEnd

    \resumeSubheading
          {\href{https://effective.af/}{Effective·AF}}{August 2023 -- October 2023}
      {Software Engineer Intern}{California, United States · Remote}
      \resumeItemListStart
        \resumeItem{Worked on adding new features to the Go GUI \textbf{Gio}.}
        \resumeItem{Refactored tons of \textbf{CLI} code for \textit{better performance} and \textit{error handling} and \textit{added} new checks and features.}
        \resumeItem{Worked with \textbf{Svelte} and \textit{added} a few components like the \textbf{left chat panel}.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/Delta456/box-cli-maker}{Box CLI Maker}} $|$ \emph{Go, ANSI Escape Code, Terminal}}{April 2020}
          \resumeItemListStart
            \resumeItem{Make Highly Customized Boxes for CLI.}
            \resumeItem{Has \textbf{400+ stars} on GitHub.}
            \resumeItem{\textit{Supports} ANSI, Tabbed, Multi-line and Line Wrapping boxes, 16 Inbuilt Colors and True Color etc.}
            \resumeItem{Used in \textbf{Kubernetes \href{https://github.com/kubernetes/minikube}{minikube}} and \textit{several} other projects.}
            \resumeItem{Featured on \href{https://golangweekly.com/}{\textbf{GoLang} \textbf{Weekly}}\textit{ twice} (\href{https://golangweekly.com/issues/340}{issue 340} and \href{https://golangweekly.com/issues/435}{issue 435}), \href{https://github.blog/2022-12-16-release-radar-nov-2022/}{\textbf{GitHub Radar}}, \href{https://githubindia.com/open-source/projects}{\textbf{GitHub India}} and \href{https://awesome-go.com/}{\textbf{Awesome Go}}.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{\href{https://github.com/vlang/v}{The V Programming Language}} $|$ \emph{V, C, Shell, Make}}{June 2019}
          \resumeItemListStart
            \resumeItem{Simple, fast, safe, compiled language for developing maintainable software.}
            \resumeItem{One of the \textbf{core developers} of the language.}
            \resumeItem{Fixed \textit{several} checker, parser, scanner, and code generation-related issues and implemented several features.}
          \resumeItemListEnd 
          \vspace{-13pt}
          \resumeProjectHeading{\textbf{\href{https://github.com/Delta456/cli_badges}{CLI Badges}} $|$ \emph{Deno, TypeScript, Terminal}}{August 2020}
           \resumeItemListStart
            \resumeItem{Generate \textit{Badges} for your apps which are \textbf{CLI-based}.}
            \resumeItem{Made in TypeScript and Deno to learn the new framework and TypeScript in general.}
            \resumeItem{Used in \textit{several} Deno projects.}
          \resumeItemListEnd
            \vspace{-13pt}       
          \resumeProjectHeading{\textbf{\href{https://github.com/Delta456/svelte-color-generator}{Svelte Color Generator}} $|$ \emph{JavaScript, Node, ViteJS, Svelte, Vercel, HTML, CSS}}{August 2023}
          \resumeItemListStart
            \resumeItem{A color generator made in \textbf{Svelte}.}
            \resumeItem{Made for learning purposes and \textbf{ported} from a React project.}
            \resumeItem{Used \textit{several} third-party components for the pop-up and color picker.}
            \resumeItem{Hosted on \href{https://svelte-color-generator-kappa.vercel.app/}{\textbf{Vercel}}.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Go, C, C++, V, JavaScript, TypeScript} \\
     \textbf{Developer Tools}{: VS Code, JetBrains IDEs, Git, Vercel, Bash, Hex Editor, Makefile} \\
     \textbf{Technologies/Frameworks}{: Linux, Svelte, Node, Deno, SQL} \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Volunteering / Extracurricular}
            \resumeItemListStart
                \resumeItem{A technical writer at \href{https://dev.to/delta456}{\textbf{Dev.to}}, and also work as a moderator for \textbf{C}, \textbf{C++} and \textbf{Go} \textit{language tags}.}
                \resumeItem{Helps in \textit{organizing events} in Delhi with \textbf{City JS India}, \textbf{PyDelhi Conference} and \textbf{FOSS United}.}
                \resumeItem{Given technical talks in many events and lightning talks at several conferences.}
                \resumeItem{Running a beginner-oriented article \textit{\href{https://github.com/Delta456/modern_cpp_series}{series}} on \textbf{C++}}
                \resumeItem{Part of NixOS (nixpkg-maintainers) and catppuccin team and contribute to their projects }
                \resumeItem{\textbf{CFP} Reviewer for \textbf{GopherCon} 2024}
            \resumeItemListEnd

            
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {KCC Institute of Technology and Management}{Sep. 2022 -- 2026}
      {Bachelors of Technology in Computer Science}{Greater Noida, Uttar Pradesh}
  \resumeSubHeadingListEnd

\end{document}
